Holomorphic field theories and higher algebra

### 2022-09-27 draft.tex
revised flavor symmetry

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

\begin{proof}[Sketch of proof]
This boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element $\sfa$ of the current algebra, which we treat as a background gauge field.

In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
This gives rise to the local anomaly
\beqn\label{eqn:electricflavor}
N \frac16 \int \op{tr}_{\underline{F}} \left(\sfa \partial \sfa \partial \sfa\right) 
\eeqn
where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.

The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
\begin{itemize}
\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
\end{itemize}
There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
\[
\check{N} \frac16 \int \op{tr}_{\Bar{\underline{F}}} \left(\sfa \partial \sfa \partial \sfa\right) .
\]
\owen{Continue from here}
Here, $\op{tr}_{\Bar{N_f}}$ denotes the trace in the anti-fundamental representation. 
There are $N_f$ copies of diagram (b) which gives rise to the term
\[
N_f \frac16\int \op{tr}_{N_f} \left(\sfa \partial \sfa \partial \sfa\right) 
\]
Since $\op{tr}_{\Bar{N_f}} (X^3) = - \op{tr}_{N_f} (X^3)$ for any $X \in \sl(N_f)$, we see that the sum of these two terms agrees with the electric side \eqref{eqn:electricflavor}.
\end{proof}

There is also a `tilded' version of the flavor symmetry for the same Lie algebra $\sl(N_f)$ but where the local Noether currents read $\int \Tilde{P}^i \Tilde{\sfa}_i^j \Tilde{Q}^i$ and $\int \Tilde{p}^i \Tilde{\sfa}_i^j \Tilde{q}^i$.
An analogous result holds for this symmetry.

>>>>

The action functional is
\[
S_{QCD} = \int B\, F^{0,2}_A + \int R \,\dbar_A Q + \int r \,\dbar_A q,
\]
where $\dbar_A = \dbar + A$ is the covariant $\dbar$-operator.
\owen{Should we make explicit how we're using the evaluation pairing on fields and their ``conjugates''? Or do we explain that in our review of BF theories?}
%We will denote this theory by $\cT(N,F)$.
\footnote{Although this perturbative theory only depends on the Lie algebra of $G$, the group structure will be relevant when we discuss local operators and moduli of vacua.} 
\end{dfn}

@@

An analogous result holds for the flavor symmetry on the antiquarks.

\begin{proof}[Sketch of proof]
The argument boils down to an explicit presentation of anomalies using the Feynman diagrammatic analysis for holomorphic theories surveyed in Section~\ref{sec:renorm}. 
For this calculation the gauge algebra $\sl(N)$ plays a minimal role. 
The central extension is represented by a series of Feynman diagrams that are wheels with three vertices, each labeled by an element of the current algebra $\sfa \in \Omega^{0,*}(\CC^2, \sl(F))$, which we treat as a background gauge field.
In formulas, we couples to both the electric and magnetic theory via interactions
\[
I^F_\sfE = \int (R, \sfa Q)  \qquad\text{and}\qquad I^F_\sfM = \int (\check{R}, \sfa \check{Q}) + \int (\check{\nu}, \sfa \check{\mu}),
\]
where we use parentheses $(-,-)$ to denote the pairings in BF and $\beta\gamma$ theories.

In the electric case there are $N$ such diagrams, with all the internal edges are labeled by $Q-R$ propagators. 
This gives rise to the local anomaly
\beqn\label{eqn:electricflavor}
 \frac{N}{16} \int \op{tr}_{\underline{F}} \left(\sfa \, \partial \sfa \, \partial \sfa\right) 
\eeqn
where $\op{tr}_{\underline{F}}$ denotes the trace in the fundamental $\sl(F)$-representation.

The magnetic theory has two types of wheels whose external edges are labeled by the background field $\sfa$: 
\begin{itemize}
\item[(a)] those with  internal edges labeled by $\check{Q}-\check{R}$ propagators and 
\item[(b)] those will internal edges labeled by $\check{\mu}-\check{\nu}$ propagators. 
\end{itemize}
There are $\check{N} = F - N$ copies of diagram (a), which gives rise to the term
\[
 \frac{\check{N}}{16} \int \op{tr}_{\underline{F}^*} \left(\sfa \, \partial \sfa \, \partial \sfa\right) .
\]
Here, $\op{tr}_{\underline{F}^*}$ denotes the trace in the dual to the fundamental representation. 
There are $F$ copies of diagram (b), which gives rise to the term
\[
\frac{F}{16}\int \op{tr}_{\underline{F}} \left(\sfa\, \partial \sfa \, \partial \sfa\right).
\]
Since $\op{tr}_{\underline{F}^*} (T^3) = - \op{tr}_{\underline{F}} (T^3)$ for any $T \in \sl(F)$, 
we see that the sum of these two terms agrees with \eqref{eqn:electricflavor} on the electric side.
\end{proof}
